\documentclass[11pt,a4paper]{moderncv}

\usepackage{verbatim}
%\usepackage{hyperref}
% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
%\definecolor{darkblue}{HTML}{EAB988}
%\definecolor{darkblue}{HTML}{9C9F84}
%\definecolor{darkblue}{HTML}{A97D5D}
\definecolor{darkblue}{HTML}{00008B}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% remove periods in title
\usepackage{xpatch}
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

% adjust the page margins
\usepackage[scale=0.85]{geometry}
\setlength{\hintscolumnwidth}{2cm}           % if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths
% personal data
\firstname{James}
\familyname{Anaipakos}
\address{New York, NY}{}    % optional, remove the line if not wanted
\mobile{+954-614-9805}                    % optional, remove the line if not wanted
\email{janaipakos@gmail.com}                      % optional, remove the line if not wanted
\homepage{jamesanaipakos.com}                % optional, remove the line if not wanted
\extrainfo{\href{http://github.com/janaipakos.com}{github.com/janaipakos}}
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
\AfterPreamble{
\hypersetup{colorlinks=true,urlcolor=darkblue,linkcolor=darkblue}
}
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

\renewcommand{\labelitemi}{$\bullet$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-40px}

\section{Summary}
\cvline{}{
\begin{itemize}%
\item Two years of experience in full-stack web development and technical editing with a focus on databases, software engineering, and anti-money laundering.
\item Project lead managing 2-6 members for an AML regulatory compliance project at a global financial institution.
\item Strong foundation in UX design, data visualization, and usability testing.
\end{itemize}
}
\vspace{-12px}
\section{Work Experience}
\cventry {2017}{Recurser}{Recurse Center}{New York, NY}{}{
\begin{itemize}
\item Self-directed study focusing on front-end development and functional programming.
\item Pair programmed on algorithms, PureScript, and Haskell.
\item Projects include image glitcher, HTTP wrapper, movie API, and JSON parser.\\
\end{itemize}
}
\vspace{-4px}
\cventry {2015--2017}{Technology Consultant}{Capco}{New York, NY}{}{
\begin{itemize}
\item Led documentation and testing enhancement for Actimize anti-money laundering application.
\item Redesigned Sharepoint 2013 customer-facing website of more than 350 pages.\\
\end{itemize}
}
\vspace{-4px}
\cventry{2015--2017}{Manuscript Reviewer}{Manning Publications}{New York, NY}{}{
\begin{itemize}
\item Tested source code, readability, and accuracy of technical manuscripts. 
\item Reviewed titles include {\em CSS in Depth}, {\em Learn Haskell}, and {\em Angular 2 in Action}.\\
\end{itemize}
}
\vspace{-4px}
\cventry{2014--2016}{WordPress Developer}{Self-Employed}{New York, NY}{}{
\begin{itemize}%
\item Created and launched several personal portfolio and sustainable goods WordPress sites.\\
\end{itemize}
}

\vspace{-12px}
\section{Education}
\cventry{2013--2015}{Pratt Institute}{}{Brooklyn, NY}{Master of Arts, Media Studies}{Graduate Coursework: Interactive Design; UX Design; Video Production; Network Communication}
\cventry{2004--2009}{Florida State University}{}{Tallahassee, FL}{Bachelor of Arts, English}{Undergraduate Coursework: Copy-Editing; Non-Fiction Writing; Interviewing}

\section{Presentations}
\cventry{2015}{NYC Media Lab Annual Summit}{}{}{QuantFlaunt Web Application}{}
\cventry{2015}{IndieCade East}{}{}{Hardware and Software in Post-Communist Central and Eastern Europe}{}

\section{Open Source}
\cvline{}{
\begin{itemize}%
\item{\href{https://ghibliapi.herokuapp.com/}{Studio Ghibli API}. Resources from Studio Ghibli films. Express, Node, JSON API.}
\item{\href{https://darksoulsnyc.herokuapp.com/}{Dark Souls NYC}. {\em Dark Souls} as Manhattan neighborhoods. MongoDB, Express, Angular.}
\item{\href{https://jamesanaipakos.com/react-d3-data-viz/}{Developer Salary Histogram}. Average developer salary by state and year. D3, React.}
\item{\href{https://jamesanaipakos.com/2015-09-01-QuantFlaunt-Overview}{QuantFlaunt}. A satirical look at branding and data quantification. Highcharts.}
\item{\href{https://jamesanaipakos.com/Marx-Magic-8-ball}{Marxist Magic 8-Ball}. Generate tweetable quotes from {\em Jacobin} magazine. jQuery.}
\end{itemize}%
}

\vspace{-12px}
\section{Technical Skills}
\cvline{}{
\begin{itemize}%
\item{Haskell, PureScript, JavaScript, HTML, CSS, Node, React, D3, Express, Webpack}
\item{SQL, PostgreSQL, MongoDB, Mongoose}
\item{UI Design, MV* Frameworks, Testing, Interviewing, Git, Adobe CS, \LaTeX}
\end{itemize}%
}
\end{document}