\documentclass[11pt,a4paper]{moderncv}


\usepackage{verbatim}
%\usepackage{hyperref}
% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
%\definecolor{darkblue}{HTML}{EAB988}
%\definecolor{darkblue}{HTML}{9C9F84}
%\definecolor{darkblue}{HTML}{A97D5D}
\definecolor{darkblue}{HTML}{4682B4}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths
% personal data
\firstname{James}
\familyname{Anaipakos}
\address{New York, NY}{}    % optional, remove the line if not wanted
\mobile{+954-614-9805}                    % optional, remove the line if not wanted
\email{janaipakos@gmail.com}                      % optional, remove the line if not wanted
\homepage{jamesanaipakos.com}                % optional, remove the line if not wanted
\extrainfo{\href{http://github.com/janaipakos.com}{github.com/janaipakos}}
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
\AfterPreamble{
\hypersetup{colorlinks=true,urlcolor=darkblue,linkcolor=darkblue}
}
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-40px}

\section{Summary}
%\vspace{-10px}
\cvline{}{
\begin{itemize}%
\item AML documentation specialist with {\textbf{four years}} of Government and Compliance experience.
\item {\textbf{Three years}} of experience as {\textbf{project leader}}, from two to six members.
\item {\textbf{One year}} of experience as technical editor in web, database, and anti-money laundering software architecture.
\item {\textbf{Nine months}} of experience in {\textbf{full-stack JavaScript development}} and testing.
\end{itemize}
\vspace{-12px}
}

\section{Experience}
\cventry {2014--Present}{Capco}{Associate Consultant}{New York, NY}{}{
\begin{itemize}%
\item Remediated portion of international bank's {\textbf{\$1.45B regulatory fine}} by stepping into project manager role mid-project and steering the documentation enhancement of an {\textbf{Actimize}} anti-money laundering application's IT components.
\item Updated documentation framework by introducing living documents in SharePoint and requirements filtering that led to a 10x reduction in effort, from {\textbf{3000}} design and testing documents to {\textbf{300}}.
\item {\textbf{AML/TxM}} program assessment and gap analysis with global standards.
\item Designed and implemented {\textbf{ETL documentation}} revamp that helped clarify the interfacing between a transaction monitoring application and 70 data warehouses.
\item Revamped and successfully-deployed Sharepoint 2013 customer-facing website with {\textbf{350+ combined pages}} while working with seven developers and designers.
\item Increased client understanding of anti-money laundering with D3, Express, and React application. 
\item Improved look and feel of Django dashboard while working with UX designer and Python developer.\\
\end{itemize}
}

\cventry{2015--Present}{Manning Publications}{Manuscript Reviewer}{New York, NY}{}{
\begin{itemize}%
\item Improve {\textbf{six titles}} prior to publication by testing source code, verifying readability, and offering feedback on reader needs. Titles include {\em CSS in Action}, {\em Learn Haskell}, and \href{https://www.manning.com/books/angular-2-in-action}{\em Angular 2 in Action}.\\
\end{itemize}
}

\cventry{2010--2012}{Department of Homeland Security}{Security Officer}{Fort Lauderdale, FL}{}{
\begin{itemize}%
\item Exhibited critical thinking, subject matter expertise, and decision making by identifying security incidents, recognizing deviating behavioral patterns, and interviewing hundreds of  passengers.
\item Passed three security drills designed to test alertness and analytical thinking.\\
\end{itemize}
}


\section{Presentations}
\cventry{2015}{NYC Media Lab Summit}{\href{https://jamesanaipakos.com/quantflaunt}{QuantFlaunt} tech demonstration}{}{}{New York, NY}
\cventry{2015}{IndieCade East}{Hardware and Software in Central and Eastern Europe}{}{}{Astoria, NY}

\section{Education}
\cventry{2013--2015}{Masters of Arts}{Media Studies}{4.0 GPA}{}{Pratt Institute, Brooklyn, NY}
\cventry{2004--2009}{Bachelors of Arts}{Double Degree, English and Humanities}{3.5 GPA}{}{Florida State University, Tallahassee, FL}

\section{Technical skills}
\cvcomputer{Compliance}{Financial Crime, TxM, AML, KYC}{Consulting}{Management, Business Analysis, Testing}
\cvcomputer{Languages}{JavaScript, C, Python, Haskell, D3, Node}{Databases}{SQL, MongoDB, Mongoose}
\end{document}