\documentclass[12pt,a4paper]{moderncv}

\usepackage{verbatim}
%\usepackage{hyperref}
% moderncv themes
\moderncvtheme[blue]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem
%\definecolor{darkblue}{HTML}{EAB988}
%\definecolor{darkblue}{HTML}{9C9F84}
%\definecolor{darkblue}{HTML}{A97D5D}
\definecolor{darkblue}{HTML}{00008B}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% remove periods in title
\usepackage{xpatch}
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

% adjust the page margins
\usepackage[scale=0.90]{geometry}
\setlength{\hintscolumnwidth}{0cm}           % if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths
% personal data
\firstname{James}
\familyname{Anaipakos}
%\address{New York, NY}{}    % optional, remove the line if not wanted
\mobile{+954-614-9805}                    % optional, remove the line if not wanted
\email{janaipakos@gmail.com}                      % optional, remove the line if not wanted
\homepage{jamesanaipakos.com}                % optional, remove the line if not wanted
\extrainfo{\href{http://github.com/janaipakos.com}{github.com/janaipakos}}
% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
\AfterPreamble{
\hypersetup{colorlinks=true,urlcolor=darkblue,linkcolor=darkblue}
}
\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

\renewcommand{\labelitemi}{$\bullet$}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle
\vspace{-50px}
\hrulefill

\section{Summary}
\vspace{-4px}
\cvline{}{
\begin{itemize}%
\item Two years of experience in front-end web development.
\item Project lead managing 2-6 members for an anti-money laundering compliance project.
\item Technical editor with a focus on databases, software engineering, and web development.
\end{itemize}
}

\vspace{-16px}
\section{Work Experience}
\vspace{-4px}
\cventry {}{Capco}{Project Manager}{NYC}{August 2015--January 2017}{
\begin{itemize}
\item Led documentation and testing enhancement for Actimize anti-money laundering web application.
\item Worked with developers to introduce living documentation and versioning in SharePoint.
\end{itemize}
}
\vspace{1px}
\cventry{}{Capco}{Web Developer}{NYC}{June 2014--August 2015}{
\begin{itemize}%
\item Worked with distributed team on front-end redesign of customer-facing website to favor mobile-first and modular components. Used JavaScript, Sass, Bootstrap, Sharepoint, JIRA.
\item Recorded and produced 20-hour knowledge transfer session covering technical architecture and codebase.
\item Created front-end for Django dashboard while working with UX designer and Python developer.
\item Redesigned dependency matrix with D3.js to help back-of-office employees track projects.
\end{itemize}
}
\vspace{1px}
\cventry{}{WordPress Developer}{Self-Employed}{}{August 2014--January 2016}{
\begin{itemize}%
\item Created and launched several personal portfolio and sustainable goods websites.
\item Clients include \href{http://barrelon.com/}{Barrel On}, \href{http://chicvilleusa.com/}{Chicville USA}, and \href{http://withpurposeandpepper.com/}{With Purpose and Pepper}.
\end{itemize}
}

\section{Personal Work}
\vspace{-4px}
\cventry {}{Recurse Center}{Recurser}{NYC}{Spring 2017}{
\begin{itemize}
\item Self-directed study focusing on front-end development, APIs, and functional programming.
\item Projects include a Haskell \href{https://github.com/janaipakos/glitcher}{image glitcher}, HTTP wrapper, and \href{https://github.com/janaipakos/ghibliapi-example}{JSON parser}.
\end{itemize}
}
\vspace{1px}
\cventry{}{Manning Publications}{Manuscript Reviewer}{}{August 2015--Present}{
\begin{itemize}
\item Test source code, readability, and accuracy for titles such as {\em React Quickly} and {\em CSS in Depth}.
\end{itemize}
}

\vspace{-2px}
\cventry{}{Open-Source Projects}{}{}{August 2015--Present}{
\begin{itemize}%
\item{\href{https://ghibliapi.herokuapp.com/}{Studio Ghibli API}. Resources from Studio Ghibli films. Express, Node, JSON API.}
\item{\href{https://github.com/janaipakos/pux-kss-pattern-library}{Pux Pattern Library}. Generate and document re-usable components. PureScript, Pux.}
\item{\href{https://darksoulsnyc.herokuapp.com/}{Dark Souls NYC}. {\em Dark Souls} as Manhattan neighborhoods. MongoDB, Express, Angular.}
\item{\href{https://jamesanaipakos.com/2015-09-01-QuantFlaunt-Overview}{QuantFlaunt}. A satirical look at branding and data quantification. Highcharts.}
\end{itemize}%
}

\section{Presentations}
\vspace{-4px}
\cvline{}{
\begin{itemize}%
\item{NYC Media Lab Annual Summit}. QuantFlaunt Web Application--{\href{https://medium.com/@justinhendrix/previewing-nyc-media-lab-s-annual-summit-demo-session-ce5169df964e}{article}}
\item{IndieCade East}. Software in Post-Communist Central and Eastern Europe--{\href{https://indiecadeeast2015.sched.com/event/2AhK}{abstract}}, {\href{https://vimeo.com/120022906}{video}}
\end{itemize}
}
\vspace{-16px}
\section{Technical Skills}
\vspace{-4px}
\cvline{}{
\begin{itemize}%
\item{JavaScript, HTML, CSS, Sass/LESS, Node, React, Express, Webpack}
\item{Haskell, PureScript, SQL, MySQL, MongoDB, Mongoose}
\item{UI Design, MV* Frameworks, Testing, Interviewing, Git, Adobe CC}
\end{itemize}%
}
\vspace{-16px}
\section{Education}
\vspace{-4px}
\cventry{}{Pratt Institute}{}{Brooklyn}{M.A. Media Studies, Fall 2013--Spring 2015}{
\begin{itemize}%
\item Graduate Coursework: Web Development; Interaction Design; Video Production; Network Communication
\end{itemize}
}
\vspace{-2px}
\cventry{}{Florida State University}{}{Tallahassee}{B.A. English, Fall 2004--Spring 2009}{}
\vspace{-2px}
\cventry{}{Scrum Alliance}{}{NYC}{Certified ScrumMaster® (CSM), Fall 2016}{
}

\end{document}
